NMRlipids Databank: Making data-driven analyses of membrane properties accessible for all

### 2022-12-06 main.tex
Update main.tex

\begin{figure}[!t]
    \centering
    \includegraphics[width=180mm]{Figures/quality3.pdf}
    \caption{ A) Best simulations ranked based on overall order parameter quality.
    B) Best simulations ranked based on the overall order parameter quality of POPE lipid. 
    C)-E) Evaluation against experimental data exemplified for a simulation with the best overall order parameter quality (C), the best quality for POPE lipid (D), and the headgroup quality for POPE (E).
    F) Scatter plots and Pearson correlation coefficients for the membrane area per lipid, thickness, first minima of x-ray scattering form factor and average order parameter of the {\it sn}-1 acyl chain extracted from the NMRlipids databank. 
    All correlation coefficients have p-value below 0.001. For more correlations see Fig.~\ref{fig:QualityCorrelationsSI}.
    }
    \label{fig:quality}
\end{figure}

@@

%best simulation, POPC with OPLS3e, is shown in
%based on C-H bond order parameters from NMR experiments and x-ray scattering form factors that enable the rapid quality evaluation of membrane MD simulations in the NMRlipids databank.

@@

%NMRlipids databank contains also experimental order parameter and x-ray form factor data that is connected to corresponding  simulations in order to define the simulation qualities and rank them to select the suitable simulation models for particular applications.

@@

 %This is demonstrated in Fig.~\ref{fig:quality} a) showing correlations between membrane lateral density (area per lipid), thickness, minima of form factor and acyl chain order analyzed from all apporimately 500 trajectories in the NMRlipids databank. Membrane area per lipid has negative correlations with membrane order and thickness with Pearson coefficient of -0.78 and -0.49, respectively, because decreased area leads to more ordered, tightly packed and stretched acyl chains leading to thicker membranes. On the other hand, locations of form factor minima have positive correlation with the membrane area and negative correlation with the thickness. In conclusion, both x-ray scattering form factors and acyl chain order parameters from NMR are on average good proxies for membrane packing and thickness, while NMR order parameters give segmental resolution information on the quality of conformational ensembles of lipids.

@@

The focus of biomolecular simulations is moving from studies of individual molecules to larger complexes and even whole cells and organelles~\cite{johnson15,thornburg22,gupta22}. On the other hand, machine learning based models predicting behaviour of biomolecules and automatic approaches to parametrize models are emerging~\cite{jumper21,antila22b}. The NMRlipids databank will support the development in all these directions. The automatic quality evaluation and ranking of simulations in the NMRlipids databank guides the optimization of new force field parameters and the selection of best parameters for large biomolecular complexes where simulation quality becomes increasingly important due the multiplication of small errors in large simulations. On the other hand, the NMRlipids databank serves as a training set for diverse machine learning applications. 
%Most straightforward applications include models that would predict connections between membrane properties that are already stored in the databank. 
For example, a machine learning model predicting electron density profiles from form factors would be highly useful in interpretation of scattering experiments. On the other hand, more elaborated models can be trained to predict arbitrary membrane properties using the data from the NMRlipids databank.

Providing programmatic access to large scale MD simulation data in the NMRlipids databank can lead to applications in unprecedented directions in fields where MD simulations are less commonly utilized. Here we exemplified this by analysing the anisotropic diffusion of water (Fig.~\ref{fig:permeability}), which is relevant in pharmacokinetic modeling and in MRI imaging where MD simulations are not yet commonly used~\cite{nitsche19,topgaard20}. 
%The NMRlipids databank will be of great benefit to scientists involved in MD simulations. They will be able to rapidly evaluate the quality of MD simulations in order to filter out potentially misleading results or facilitate force field parameter development~\cite{antila22b}. The selection of best models for a specific application is demonstrated for PC/PE lipid mixtures in Fig.~\ref{fig:quality}, and previously for PC/PS lipid mixtures~\cite{antila22b}, and lipid headgroups~\cite{bacle21}. 
On the other hand, programmatic access in the NMRlipids databank enables automatic analyses over larger sets of simulation data in terms of quantity (e.g., simulation length and number of conformations) and content (e.g, lipid compositions and ion concentrations) that is currently possible in a single research group. Added value of such access to simulation data is demonstrated here for the analysis of simulation qualities (Fig.~\ref{fig:quality}), water permeation through membranes (Fig.~\ref{fig:permeability}) and cholesterol flip-flop events (Fig.~\ref{fig:flip-flops}). 
%Such models could be used to connect membrane composition to relevant membrane properties in wide range of fields from molecular biology to drug development and biomolecular imaging. 
Different types of applications enabled by the NMRlipids databank in wide range of fields are exemplified in Table~\ref{tab:applications}. The increasing amount of data is expected to further increase the scope of potential applications of the NMRlipids databank in wide range of fields ranging from molecular biology and biotechnology to
%the design of lipid nanoparticles for drug delivery or other applications, and 
material science and biomolecular imaging.

@@

Main practical limitations in building open access databanks of molecular dynamics simulations have been the required commitment in long term support for hardware and software maintenance, and the lack of incentives for researchers to share the data. The NMRlipids databank circumvents these challenges with the overlay databank design and open collaboration approach developed in the NMRlipids project~\cite{botan15}. In this model, the file storage is distributed to publicly available stable repositories ({\it Data layer} in Fig.~\ref{fig:overlay} A) and maintenance of the databank does not depend on individual scientists or groups because all its version controlled content is available with an open access licence ({\it Databank layer} in Fig.~\ref{fig:overlay} A). 
%containing relevant information about the trajectories, including the location of the raw data. This architecture streamlines the construction and maintenance of the databank
%
%, the demand of hardware can be distributed and open collaboration model reduces the risk for ending software maintenance. 
%Furthermore, the 
%by distributing the long term commitment for hardware and software maintenance. 
Incentive to share the data is created in the NMRlipids open collaboration by offering authorship in published articles to the contributors following the NMRlipids project protocol~\cite{botan15}.
%, thereby creating an incentive for contributions. 
%
%Universal quality measures and naming conventions for molecules and atoms are defined in the NMRlipids databank to enable the automatic quality evaluation and other analyses.
%
%of lipid bilayer MD simulations introduced in the NMRlipids databank enables rapid ranking of available simulation models agains experimental NMR and x-ray scattering data. 
%
The current NMRlipids databank contains only lipid bilayer simulations, but the concept can be applied also to other biomolecules, such as disordered proteins and membrane-protein systems,
%combining open collaboration and overlay databank structure can be applied also 
or other fields where similar barriers to establish publicly accessible databanks exist. 
%The overlay databank design can open such avenues also for other

@@

\subsection{Adding data into the NMRlipids databank}
The NMRlipids databank is open for additions of simulation data by anyone. The first step is to create an info.yaml file containing the information that needs to be manually entered as listed in table~\ref{tab:READMEkeys}. This file can be then added into {\it /Scripts/BuildDatabank/info\_files} folder in the NMRlipids databank repository via pull requests. After the pull request is manually accepted, the rest of the information for the README.yaml file, listed in table~\ref{tab:READMEkeys}, will be automatically extracted using the {\it /Scripts/BuildDatabank/AddData.py} script. Currently the NMRlipids databank is composed of simulations found from Zenodo repository with an appropriate licence. Most, but not all, of these trajectories originate from previous NMRlipids projects~\cite{botan15,catte16,antila19,bacle21}.

\subsection{Experimental data}
Experimental data used in the quality evaluation, currently composed of C-H bond order parameters and x-ray scattering form factors, are stored in {\it /Data/experiments} in the NMRlipids databank repository. Similarly to simulations, each experimental data set has a README.yaml file containing all the relevant information about the experiment. The keys and their descriptions for the experimental data are given in table~\ref{tab:READMEkeysEXP}. NMR data currently in the NMRlipids databank are taken from Refs.~\citenum{scherer87,ferreira13,antila19,melcr20,bacle21} and x-ray scattering data from Refs.~\citenum{Kucerka08a,kucerka11,pan12b,pan14,kucerka15}. In addition, some previously unpublished NMR and x-ray scattering data are used. These are measured with previously established methods as described in the supplementary information.

@@

\subsection{Calculation of x-ray scattering form factors}
X-ray scattering form factors were calculated with standard equation for symmetric lipid bilayers~\cite{ollila16}
\begin{equation}\label{FFsimpl}
F(q)=\int_{-D/2}^{D/2}\Delta \rho_e(z) \cos(zq_z) {\rm d}z,
\end{equation}
where $\Delta \rho_e(z)$ is the difference between total and solvent electron densities, and $D$ is the simulation box size in the z-direction. For the calculation of density profiles, atom coordinates were first centred around the centre of mass of lipid molecules for every time frame, and a histogram of these centred positions weighted with the number of electrons in each atom was then calculated with the bin width of $1/3$~Å. 
%Similarly to order parameters, the script loops over all simulations, downloads the data on local computer, and uses the information in README.yaml file to calculate form factors. 
The script to calculate form factors for all simulations in the NMRlipids databank is available at {\it Scripts/AnalyzeDatabank/calc\_FormFactors.py}. The resulting form factors are stored for all simulations in files named {\it FormFactor.json} at folders in {\it /Data/Simulations} in the NMRlipids databank repository.

@@

\subsection{Quality evaluation of x-ray scattering form factors}
%While C-H bond order parameters relate to the conformational ensembles of individual lipids, the x-ray scattering form factors depend on membrane dimensions and density distribution~\cite{ollila16}.
Because experiments give form factors only in relative intensity scale, they should scaled before comparing with the simulation data. Here we use the scaling coefficient for experimental intensities defined in the SIMtoEXP program~\cite{kucerka10}
\begin{equation}
    k_e = \frac{\sum_{i=1}^{N_q} \frac{|F_s(q_i)||F_e(q_i)|}{(\Delta F_e(q_i))^2}}{\sum_{i=1}^{N_q} \frac{|F_e(q_i)|^2}{(\Delta F_e(q_i))^2}},
\end{equation}
%The quality of each form factor was then calculated from the equation
%\begin{equation}
%    \chi^2 = \frac{\sqrt{\sum_{i=1}^{N_q}(|F_s(q_i)|-k_e|F_e(q_i)|)^2/(\Delta F_e(q_i))^2}}{\sqrt{N_q-1}},
%\end{equation}
where $F_s(q)$ and $F_e(q)$ are form factors from a simulation and experiment, respectively, $\Delta F_e(q)$ is the error of the experimental form factor, and summation goes over the experimentally available $N_q$ points.

Also a quality measure based on differences in simulated and experimental form factors accross available q-range is defined in the SIMtoEXP program~\cite{kucerka10}. However, the lobe heigths in simulated form factors depend on the simulation box size as shown in Fig.~\ref{fig:sizedependence}. Therefore, the quality measure defined in SIMtoEXP  would also depend on the simulation box size. Nevertheless, locations of form factor minima are independent on simulation box size in Fig.~\ref{fig:sizedependence}. Here we use the location of the first form factor minima for the quality evaluation because automatic detection of the location of second minima is inaccurate for some experimental data due to fluctuations, such as for the POPE data in Figs.~\ref{fig:quality} D and E. 
%In order to define a quality measure which is independent on simulation box size, we measure the form factor quality based on the location of the first minima observed in experiments. 
The first minimum correlates well with the thickness of a membrane (Fig.~\ref{fig:quality} F), although the correlation of the second minima would be even stronger (Fig.~\ref{fig:QualityCorrelationsSI}). In practise, we first filter the fluctuations from the form factor data using Savitzky-Golay filter (window lenght 30 and polynomial order 1) and locate the first minima above 0.1\,\AA$^{-1}$ from both simulation and experimental data. The quality of a form factor is then defined as Eucledian distance between the minima in simulated and experimental form factors, $FF_q = |FF_{\rm{min}}^{\rm{sim}}-FF_{\rm{min}}^{\rm{exp}}|$.

@@

\subsection{Calculation of lipid flip-flops}
Flip-flop rates were calculated using {\it AssignLeaflets} and {\it FlipFlop} tools from LiPyphilic package~\cite{LiPyphilic2021}. Headgroup atoms of each molecule as defined in the mapping file were used to determine in which leaflet the molecule locates. The midplane cut-off defining the region between leaflets was 1\,nm and frame cut-off was 100. This means that if the headgroup of a molecule entered within the distance of 1\,nm from the bilayer midplane and was found from the opposing leaflet after 100 steps, this event was considered as a successfull flip-flop event. The code that finds flip-flop events from all simulations in the NMRlipids databank is available at {\it scripts/FlipFlop.py} and the results at {\it Data/Flipflops/} in the repository at~\url{https://github.com/NMRLipids/DataBankManuscript/}.

>>>>

\begin{figure}[!t]
    \centering
    \includegraphics[width=180mm]{Figures/quality3.pdf}
    \caption{ A) Best simulations ranked based on overall order parameter quality.
    B) Best simulations ranked based on the overall order parameter quality of POPE lipid. 
    C)-E) Evaluation against experimental data exemplified for a simulation with the best overall order parameter quality (C), the best quality for POPE lipid (D), and the headgroup quality for POPE (E).
    F) Scatter plots and Pearson correlation coefficients for the membrane area per lipid, thickness, first minima of X-ray scattering form factor and average order parameter of the {\it sn}-1 acyl chain extracted from the NMRlipids databank. 
    All correlation coefficients have p-value below 0.001. For more correlations see Fig.~\ref{fig:QualityCorrelationsSI}.
    }
    \label{fig:quality}
\end{figure}

@@

%best simulation, POPC with OPLS3e, is shown in
%based on C-H bond order parameters from NMR experiments and X-ray scattering form factors that enable the rapid quality evaluation of membrane MD simulations in the NMRlipids databank.

@@

%NMRlipids databank contains also experimental order parameter and X-ray form factor data that is connected to corresponding  simulations in order to define the simulation qualities and rank them to select the suitable simulation models for particular applications.

@@

 %This is demonstrated in Fig.~\ref{fig:quality} a) showing correlations between membrane lateral density (area per lipid), thickness, minima of form factor and acyl chain order analyzed from all apporimately 500 trajectories in the NMRlipids databank. Membrane area per lipid has negative correlations with membrane order and thickness with Pearson coefficient of -0.78 and -0.49, respectively, because decreased area leads to more ordered, tightly packed and stretched acyl chains leading to thicker membranes. On the other hand, locations of form factor minima have positive correlation with the membrane area and negative correlation with the thickness. In conclusion, both X-ray scattering form factors and acyl chain order parameters from NMR are on average good proxies for membrane packing and thickness, while NMR order parameters give segmental resolution information on the quality of conformational ensembles of lipids.

@@

The focus of biomolecular simulations is moving from studies of individual molecules to larger complexes and even whole cells and organelles~\cite{johnson15,thornburg22,gupta22}. Simultaneously, machine learning-based models predicting behaviour of biomolecules and automatic approaches to parametrize models are emerging~\cite{jumper21,antila22b}. The NMRlipids databank will support the development in all these directions. The automatic quality evaluation and ranking of simulations in the NMRlipids databank guides the optimization of new force field parameters and the selection of best parameters for large biomolecular complexes where simulation quality becomes increasingly important due the accumulation of small errors in large simulations. Furthermore, the NMRlipids databank serves as a training set for diverse machine learning applications. 
%Most straightforward applications include models that would predict connections between membrane properties that are already stored in the databank. 
For example, a machine learning model predicting electron density profiles from form factors would be highly useful in interpretation of scattering experiments. In addition, more elaborated models can be trained to predict arbitrary membrane properties using the data from the NMRlipids databank.

Providing programmatic access to large scale MD simulation data in the NMRlipids databank can lead to applications in unprecedented directions in fields where MD simulations are less commonly utilized. Here, we exemplified this by analysing the anisotropic diffusion of water (Fig.~\ref{fig:permeability}), which is relevant in pharmacokinetic modeling and in MRI imaging, both areas where MD simulations are not yet commonly used~\cite{nitsche19,topgaard20}. 
%The NMRlipids databank will be of great benefit to scientists involved in MD simulations. They will be able to rapidly evaluate the quality of MD simulations in order to filter out potentially misleading results or facilitate force field parameter development~\cite{antila22b}. The selection of best models for a specific application is demonstrated for PC/PE lipid mixtures in Fig.~\ref{fig:quality}, and previously for PC/PS lipid mixtures~\cite{antila22b}, and lipid headgroups~\cite{bacle21}. 
The programmatic access in the NMRlipids databank enables automatic analyses over larger sets of simulation data in terms of quantity (e.g., simulation length and number of conformations) and content (e.g, lipid compositions and ion concentrations) than is currently possible by a single research group. The added value that access to this simulation data provides is demonstrated here for the analysis of simulation qualities (Fig.~\ref{fig:quality}), water permeation through membranes (Fig.~\ref{fig:permeability}) and cholesterol flip-flop events (Fig.~\ref{fig:flip-flops}). 
%Such models could be used to connect membrane composition to relevant membrane properties in wide range of fields from molecular biology to drug development and biomolecular imaging. 
Different types of applications enabled by the NMRlipids databank across a wide range of fields are exemplified in Table~\ref{tab:applications}. The ever growing amount of data is expected to further increase the scope of potential applications of the NMRlipids databank in molecular biology, biotechnology, 
%the design of lipid nanoparticles for drug delivery or other applications, and 
material science, biomolecular imaging and beyond.

@@

The main practical limitations in building open access databanks of molecular dynamics simulations have been the required commitment in long term support for hardware and software maintenance, and the lack of incentives for researchers to share the data. The NMRlipids databank circumvents these challenges with the overlay databank design and open collaboration approach developed in the NMRlipids project~\cite{botan15}. In this model, the file storage is distributed to publicly available stable repositories ({\it Data layer} in Fig.~\ref{fig:overlay} A) and maintenance of the databank does not depend on individual scientists or groups because all its version-controlled content is available with an open access licence ({\it Databank layer} in Fig.~\ref{fig:overlay} A). 
%containing relevant information about the trajectories, including the location of the raw data. This architecture streamlines the construction and maintenance of the databank
%
%, the demand of hardware can be distributed and open collaboration model reduces the risk for ending software maintenance. 
%Furthermore, the 
%by distributing the long term commitment for hardware and software maintenance. 
Incentive to share the data is created in the NMRlipids open collaboration by offering authorship in published articles to the contributors following the NMRlipids project protocol~\cite{botan15}.
%, thereby creating an incentive for contributions. 
%
%Universal quality measures and naming conventions for molecules and atoms are defined in the NMRlipids databank to enable the automatic quality evaluation and other analyses.
%
%of lipid bilayer MD simulations introduced in the NMRlipids databank enables rapid ranking of available simulation models agains experimental NMR and X-ray scattering data. 
%
The current NMRlipids databank contains only lipid bilayer simulations, but the concept can also be applied to other biomolecules, such as disordered proteins and membrane-protein systems,
%combining open collaboration and overlay databank structure can be applied also 
or other fields where similar barriers to establish publicly accessible databanks exist. 
%The overlay databank design can open such avenues also for other

@@

\subsection{Adding data into the NMRlipids databank}
The NMRlipids databank is open for additions of simulation data by anyone. The first step is to create an info.yaml file containing the information that needs to be manually entered as listed in table~\ref{tab:READMEkeys}. This file can be then added into {\it /Scripts/BuildDatabank/info\_files} folder in the NMRlipids databank repository via pull requests. After the pull request is manually accepted, the rest of the information for the README.yaml file, listed in table~\ref{tab:READMEkeys}, will be automatically extracted using the {\it /Scripts/BuildDatabank/AddData.py} script. Currently, the NMRlipids databank is composed of simulations found from Zenodo repository with an appropriate licence. Most, but not all, of these trajectories originate from previous NMRlipids projects~\cite{botan15,catte16,antila19,bacle21}.

\subsection{Experimental data}
Experimental data used in the quality evaluation, currently composed of C-H bond order parameters and X-ray scattering form factors, are stored in {\it /Data/experiments} in the NMRlipids databank repository. Similarly to simulations, each experimental data set has a README.yaml file containing all the relevant information about the experiment. The keys and their descriptions for the experimental data are given in table~\ref{tab:READMEkeysEXP}. NMR data currently in the NMRlipids databank are taken from Refs.~\citenum{scherer87,ferreira13,antila19,melcr20,bacle21} and X-ray scattering data from Refs.~\citenum{Kucerka08a,kucerka11,pan12b,pan14,kucerka15}. In addition, some previously unpublished NMR and X-ray scattering data are used. These are measured with previously established methods as described in the supplementary information.

@@

\subsection{Calculation of X-ray scattering form factors}
X-ray scattering form factors were calculated with standard equation for symmetric lipid bilayers~\cite{ollila16}
\begin{equation}\label{FFsimpl}
F(q)=\int_{-D/2}^{D/2}\Delta \rho_e(z) \cos(zq_z) {\rm d}z,
\end{equation}
where $\Delta \rho_e(z)$ is the difference between total and solvent electron densities, and $D$ is the simulation box size in the z-direction. For the calculation of density profiles, atom coordinates were first centred around the centre of mass of lipid molecules for every time frame, and a histogram of these centred positions weighted with the number of electrons in each atom was then calculated with the bin width of $1/3$~Å. 
%Similarly to order parameters, the script loops over all simulations, downloads the data on local computer, and uses the information in README.yaml file to calculate form factors. 
The script to calculate form factors for all simulations in the NMRlipids databank is available at {\it Scripts/AnalyzeDatabank/calc\_FormFactors.py}. The resulting form factors are stored for all simulations in files named {\it FormFactor.json} at folders in {\it /Data/Simulations} in the NMRlipids databank repository.

@@

\subsection{Quality evaluation of X-ray scattering form factors}
%While C-H bond order parameters relate to the conformational ensembles of individual lipids, the X-ray scattering form factors depend on membrane dimensions and density distribution~\cite{ollila16}.
Because experiments give form factors only in relative intensity scale, they should scaled before comparing with the simulation data. Here we use the scaling coefficient for experimental intensities defined in the SIMtoEXP program~\cite{kucerka10}
\begin{equation}
    k_e = \frac{\sum_{i=1}^{N_q} \frac{|F_s(q_i)||F_e(q_i)|}{(\Delta F_e(q_i))^2}}{\sum_{i=1}^{N_q} \frac{|F_e(q_i)|^2}{(\Delta F_e(q_i))^2}},
\end{equation}
%The quality of each form factor was then calculated from the equation
%\begin{equation}
%    \chi^2 = \frac{\sqrt{\sum_{i=1}^{N_q}(|F_s(q_i)|-k_e|F_e(q_i)|)^2/(\Delta F_e(q_i))^2}}{\sqrt{N_q-1}},
%\end{equation}
where $F_s(q)$ and $F_e(q)$ are form factors from a simulation and experiment, respectively, $\Delta F_e(q)$ is the error of the experimental form factor, and summation goes over the experimentally available $N_q$ points.

Also, a quality measure based on differences in simulated and experimental form factors accross available q-range is defined in the SIMtoEXP program~\cite{kucerka10}. However, the lobe heigths in simulated form factors depend on the simulation box size as shown in Fig.~\ref{fig:sizedependence}. Therefore, the quality measure defined in SIMtoEXP  would also depend on the simulation box size. Nevertheless, locations of form factor minima are independent on simulation box size in Fig.~\ref{fig:sizedependence}. Here we use the location of the first form factor minima for the quality evaluation because automatic detection of the location of second minima is inaccurate for some experimental data due to fluctuations, such as for the POPE data in Figs.~\ref{fig:quality} D and E. 
%In order to define a quality measure which is independent on simulation box size, we measure the form factor quality based on the location of the first minima observed in experiments. 
The first minimum correlates well with the thickness of a membrane (Fig.~\ref{fig:quality} F), although the correlation of the second minima would be even stronger (Fig.~\ref{fig:QualityCorrelationsSI}). In practise, we first filter the fluctuations from the form factor data using Savitzky-Golay filter (window lenght 30 and polynomial order 1) and locate the first minima above 0.1\,\AA$^{-1}$ from both simulation and experimental data. The quality of a form factor is then defined as Eucledian distance between the minima in simulated and experimental form factors, $FF_q = |FF_{\rm{min}}^{\rm{sim}}-FF_{\rm{min}}^{\rm{exp}}|$.

@@

\subsection{Calculation of lipid flip-flops}
Flip-flop rates were calculated using {\it AssignLeaflets} and {\it FlipFlop} tools from LiPyphilic package~\cite{LiPyphilic2021}. Headgroup atoms of each molecule as defined in the mapping file were used to determine in which leaflet the molecule locates. The midplane cut-off defining the region between leaflets was 1\,nm and frame cutoff was 100. This means that if the headgroup of a molecule entered within the distance of 1\,nm from the bilayer midplane and was found from the opposing leaflet after 100 steps, this event was considered as a successfull flip-flop event. The code that finds flip-flop events from all simulations in the NMRlipids databank is available at {\it scripts/FlipFlop.py} and the results at {\it Data/Flipflops/} in the repository at~\url{https://github.com/NMRLipids/DataBankManuscript/}.
